{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2014-12-15 brains-introduction.tex
Add references for awkward/common jury

Less classical linguistic variables, based on the study of semantic network properties, have recently started to be used, in the context of connectionism and its normative processual models (see for instance \citet{collins1975spreading}).
Let us mention two interesting studies on that matter, which demonstrate in a strictly \emph{in vitro} framework and at the vocabulary level that word properties computed on a word network are important factors for the cognitive processes and reproduction of those words.
First, \citet{Griffiths07} analyze a task where subjects are asked to name the first word which comes to their mind when they are presented with a random letter from the %Latin
alphabet. The authors show that there exists a link between the ease of recall of words and one of their semantic features, namely their authority position (PageRank) in a language-wide semantic network built from external word association data.
A second psycholinguistic study by \citet{Chan10} shows, in a picture-naming task, that words are produced faster and with fewer mistakes when they have a lower clustering coefficient in an underlying phonological network (which, again, is  defined from external phonological data).
\rk{add \url{https://www.sciencedirect.com/science/article/pii/S0893608012000330}, \url{http://research.clps.brown.edu/austerweil/pdfs/papers/randomWalkNips2012.pdf}, \url{http://link.springer.com/article/10.3758/s13421-013-0312-y} to that picture}

On the whole, the current psycholinguistic state-of-the-art seems to hint towards two antagonistic types of results.
On one hand, part of the literature tends to show that recall is easier for the least ``awkward'' words; those whose age of acquisition is earlier, length is smaller, semantic network position is more central -- this is particularly true in tasks where participants are asked to form spontaneous associations or utter a word in response to a given signal \CN.
On the other hand, when the task consists in remembering a specific list of items, ``awkward'' words are actually more easily remembered, possibly as they are more informative and plausibly more discernible \CN.
The jury is still out as to whether reformulation alteration, i.e. spontaneous replacement of words when asked to repeat a given utterance, is rather of the former or latter sort.
We also aim here at shedding some light on this debate, considering oddness as a dimension of the purported fitness of utterances.

>>>>

Less classical linguistic variables, based on the study of semantic network properties, have recently started to be used, in the context of connectionism and its normative processual models (see for instance \citet{collins1975spreading} for an example of such models).
Let us mention two interesting studies on that matter, which demonstrate in a strictly \emph{in vitro} framework and at the vocabulary level that word properties computed on a word network are important factors for the cognitive processes and reproduction of those words.
First, \citet{Griffiths07} analyze a task where subjects are asked to name the first word which comes to their mind when they are presented with a random letter from the %Latin
alphabet. The authors show that there exists a link between the ease of recall of words and one of their semantic features, namely their authority position (PageRank) in a language-wide semantic network built from external word association data.
A second psycholinguistic study by \citet{Chan10} shows, in a picture-naming task, that words are produced faster and with fewer mistakes when they have a lower clustering coefficient in an underlying phonological network (which, again, is  defined from external phonological data).
\rk{add \url{https://www.sciencedirect.com/science/article/pii/S0893608012000330}, \url{http://research.clps.brown.edu/austerweil/pdfs/papers/randomWalkNips2012.pdf}, \url{http://link.springer.com/article/10.3758/s13421-013-0312-y} to that picture}

On the whole, the current psycholinguistic state-of-the-art seems to hint towards two antagonistic types of results.
On one hand, part of the literature tends to show that recall is easier for the least ``awkward'' words; those whose age of acquisition is earlier, length is smaller, semantic network position is more central -- this is particularly true in tasks where participants are asked to form spontaneous associations or utter a word in response to a given signal.
On the other hand, when the task consists in recognizing a specific item in a list, ``awkward'' words are actually more easily remembered, possibly as they are more informative and plausibly more discernible (see again~\citet{Yonelinas02} for a review).
The jury is still out as to whether reformulation alteration, i.e. spontaneous replacement of words when asked to repeat a given utterance, is rather of the former or latter sort.
We also aim here at shedding some light on this debate, considering oddness as a dimension of the purported fitness of utterances.
